Meaningful data sharing

### 2020-09-23 new-paper.Rmd
minor changes - removed hanging text on "other bit to say" and minor adjustment to license section

```{=tex}
\begin{singlespace}
Other titles under consideration:

- Data sharing practices to realign incentives and enable positive/meaningful culture change

- Enabling culture change for meaningful data sharing

- Enabling culture change for meaningful data sharing: Aligning incentives and minimally acceptable practices

- Principles of sharing data

- Elements of meaningful data sharing

- Better practices in data sharing to enable culture change

@@

**note: other little bit to say**

- "Here are some high level ideas on how to share data, that might obvious but are not often considered"

@@

Provide a license with your data. A license for data establishes the rules for its use, and whether it can be modified or shared. Without a license, or with a non-standard one, these rules are unclear, and can lead to issues with use, attribution and citation. While there are a handful of licenses for data [@data_world_inc_common_2019], we recommend the CC0 license, as it provides simple rules for attribution, warranty, and use, and is very common. The CC0 allows data owners to waive all rights and data licensed as such can be freely shared, copied, modified, and distributed, even for commercial purposes without permission.  For more information on the benefit of using CC0, and why CCBY is not always appropriate, see https://osc.universityofcalifornia.edu/2016/09/cc-by-and-data-not-always-a-good-fit/. Short and full overviews of CCBY and CC0 can be found at [@cc0-short; @cc0-long].

>>>>

Other titles under consideration:

- Data sharing practices to realign incentives and enable positive/meaningful culture change\\
- Enabling culture change for meaningful data sharing\\
- Enabling culture change for meaningful data sharing: Aligning incentives and minimally acceptable practices\\
- Principles of sharing data\\
- Elements of meaningful data sharing\\
- Minimally acceptable practices in data sharing to enable culture change\\

@@

@@

Provide a license file with your data. A license for data establishes the rules for its use, and whether it can be modified or shared. Without a license, or with a non-standard one, these rules are unclear, and can lead to issues with use, attribution and citation. While there are a handful of licenses for data [@data_world_inc_common_2019], we recommend the CC0 license, as it provides simple rules for attribution, warranty, and use, and is very common. The CC0 means data owners waive all rights and data licensed as such can be freely shared, copied, modified, and distributed, without permission or attribution, even for commercial purposes.  For more information on the benefit of using CC0, and why CCBY is not always appropriate, see https://osc.universityofcalifornia.edu/2016/09/cc-by-and-data-not-always-a-good-fit/. Short and full overviews of CC0 can be found at @cc0-short and @cc0-long.
